Masters Thesis

### 2011-09-14 docs/thesis/sources/literature_survey.tex
Added figures and updated thesis.tex

\section{Literature Survey}\label{section:litsurvey}
\subsection{Time Synchronization}
Time synchronization has been the subject of research for many years.

@@

\subsection{Similar Work}
In order to determine the improvements of novel methods, reference systems need to be available to compare with. Both~\cite{mac:tdma}~and~\cite{mac:lowdutycycle} provide a suitable reference system for a synchronized, non-relaying BSN. Both proposed systems present, in detail, a TDMA MAC protocol specifically designed with energy efficiency in mind. Details of packet format, TDMA frame calculation, and power consumption measurements are available.
%Add more details later

>>>>

\section{Previous Work}\label{section:litsurvey}
\subsection{Time Synchronization}
Time synchronization has been the subject of research for many years.

@@

%\subsection{Similar Work}
%In order to determine the improvements of novel methods, reference systems need to be available to compare with. Both~\cite{mac:tdma}~and~\cite{mac:lowdutycycle} provide a suitable reference system for a synchronized, non-relaying BSN. Both proposed systems present, in detail, a TDMA MAC protocol specifically designed with energy efficiency in mind. Details of packet format, TDMA frame calculation, and power consumption measurements are available.
%Add more details later

### 2011-09-14 docs/thesis/thesis.tex
Added figures and updated thesis.tex

\documentclass{article}
\usepackage{graphicx}
\begin{document}
\title{Masters Thesis}
\author{Alvaro Prieto}
\maketitle

@@

\section{Introduction}

% Include literature survey from other file
\input{sources/literature_survey} %uncomment to include literature survey

@@

The three main parts of the project are: 
\begin{itemize}
\item Developing the analog front-end to measure the biopotential signals from the subject.
\item Developing the software/firmware libraries to measure, store, and transmit the data from the EDs to the host.
\item Developing the lead reconstruction algorithms to convert the 3 measurements back to a physician friendly 12-lead display.
\end{itemize}
The work presented here focuses on the software/firmware development for the application.

\subsection{TinyOS Platform}
The first wireless ECG platform was developed using the Imperial College London BSN Motes running TinyOS. These devices

\subsection{CC430 Platform}

@@

While many, more precise, time synchronization methods are available~\cite{synchronization:FTSP}, it was determined that they were not needed. Due to the low sampling rate and the use of crystal oscillators to run the timers, the precision obtained with this simple method was good enough for the system. More complex methods would not have significantly improved results.

@@

\subsection{Host Interface}

\section{Conclusion}

>>>>

\documentclass{article}
\usepackage{graphicx}
\begin{document}
\title{Masters Thesis}
\author{Alvaro Prieto\\
BS/MS Electrical Engineering\\
\texttt{axp8664@rit.edu}}
\maketitle

@@

\begin{abstract}
...
\end{abstract}

\section{Summary of Contributions}
\begin{itemize}
\item BSN Software Libraries
\item wireless ECG platform
\item New routing algorithm
\end{itemize}
% Include literature survey from other file
\input{sources/literature_survey} %uncomment to include literature survey

@@

The three main parts of the wireless ECG project are: 
\begin{itemize}
\item Developing the analog front-end to measure the biopotential signals from the subject.
\item Developing the software/firmware libraries to measure, store, and transmit the data from the EDs to the host.
\item Developing the lead reconstruction algorithms to convert the 3 measurements back to a physician friendly 12-lead display.
\end{itemize}
The work presented here focuses on the software/firmware development for the application.

\subsection{TinyOS Platform}
The first wireless ECG platform was developed using the Imperial College London BSN Motes, which use the TinyOS operating system. These devices are programmed in a derivative of the C language called NesC. While working with these devices and operating system was not particularly simple, the hardware worked, and had been used in other projects. A full 3-sensor wireless ECG application (minus the lead reconstruction) was implemented with these devices. Since the devices run an operating system, several, non-ideal, modifications were required to obtain precise time synchronization.

\subsection{CC430 Platform}
After demonstrating the system using the TinyOS devices, the development of the in-house system continued. After several hardware implementations, a similar 3-sensor wireless ECG application was developed. In contrast to the TinyOS system, the CC430 platform only used hardware and software that was developed by the team.

@@

While many, more precise, time synchronization methods are available~\cite{synchronization:FTSP}, it was determined that they were not needed. Due to the low sampling rate and the use of crystal oscillators to run the timers, the precision obtained with this simple method was good enough for the system. More complex methods would not have significantly improved results. Figure~\ref{fig:sync_data} shows the result of three separate wireless devices measuring the same signal. This method was used to confirm that the samples were aligned.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.8\textwidth]{figures/syncdata.pdf}
\end{center}
\caption{Synchronization Test}
\label{fig:sync_data}
\end{figure}

@@

\subsection{Host Interface}
The primary focus of this project was to obtain synchronized samples from several wireless devices. A secondary, but important, goal was to display the data in real time. To speed up development, the live-plotting tool kst(http://kst-plot.kde.org/) was used. A application, written in C, communicated via a USB-to-Serial link with the AP and received all of the ED data. It then output the data to CSV files, which were then used as an input for kst. Figure~\ref{fig:heartbeats} shows an ECG lead wirelessly measured from a human subject.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=1\textwidth]{figures/heartbeats.pdf}
\end{center}
\caption{Sample Measurement from Single ECG Lead}
\label{fig:heartbeats}
\end{figure}

\section{Conclusion}
...

\listoffigures

%\listoftables
